---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Victoria Force"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 6
    fig_width: 6
    highlight: espresso
    theme: cerulean
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns. The variables are dataset, x, and y.

### Exercise 2


Plotting the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, clean up the narrative by removing these instructions.)

Plotting the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation between x and y in the star dataset:

```{r cor-star}
star_data %>%
  summarize(r=cor(x,y))
```
The correlation between x and y in star is .002 higher that the correlation between x and y in dino.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor circle}
circle_data %>%
  summarize(r=cor(x,y))
```
The correlation between x and y in circle is .004 lower than the correlation between x and y in dino.

### Exercise 5

```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarise(r=cor(x,y)) %>%
  print(13)
```